% !TEX program = xelatex
\documentclass[11pt,a4paper]{article}

% ----------------------------------------------------
% Preamble inspired by popular Overleaf resume templates
% ----------------------------------------------------
\usepackage{geometry}
\geometry{left=1.6cm,right=1.6cm,top=1.6cm,bottom=1.6cm}

\usepackage{fontspec}
\setmainfont{TeX Gyre Termes}
\setsansfont{TeX Gyre Heros}
\setmonofont{TeX Gyre Cursor}

\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=black
}

\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries\sffamily}{\thesection}{0.5em}{}
\titlespacing*{\section}{0pt}{1.2ex}{0.8ex}

\setlist[itemize]{leftmargin=*,nosep}

\newcommand{\resumeSection}[1]{\section*{#1}\vspace{-0.5em}\hrule\vspace{0.6em}}
\newcommand{\resumeSubsection}[4]{
  \textbf{#1} \hfill {#2}\\
  \textit{#3} \hfill {#4}
}
\newcommand{\resumeItem}[1]{\item #1}

\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE \textbf{Xiaoyuan Zhang}}\\[4pt]
  \href{tel:+8615568818289}{+86 155-6881-8289} $\vert$
  \href{mailto:15568818289@163.com}{15568818289@163.com} $\vert$
  Unit~29, Building~16, Yucui Haoting, Fanrong Road, Yatai Street,\\
  Nanguan District, Changchun, Jilin Province, 130000\\[6pt]
  \textit{Aspiring ESSEC Master in Luxury Management candidate passionate about bridging data-driven insights with premium brand storytelling.}
\end{center}

\vspace{0.5em}

\resumeSection{Education}
\resumeSubsection{Renmin University of China}{Suzhou, China}{Bachelor of Science in Finance}{Sep.~2022 -- Jul.~2026}
\begin{itemize}
  \resumeItem{GPA: 3.6/4.0; 985 \& 211 Projects university.}
  \resumeItem{Relevant Coursework: Econometrics, Statistics, Application Methods and Data Analysis, Budget Control and Supply Chain, Management, Marketing, French.}
\end{itemize}
\vspace{0.4em}
\resumeSubsection{KEDGE Business School}{Bordeaux, France}{Bachelor Exchange in Marketing}{Jun.~2024 -- Jun.~2025}
\begin{itemize}
  \resumeItem{GPA: 15.77/20.}
  \resumeItem{Relevant Coursework: Luxury Marketing, Business Data Analysis, Marketing Strategy, Digital Marketing, Company Strategic Diagnosis, Simulated Operations and Management.}
\end{itemize}

\resumeSection{Professional Experience}
\resumeSubsection{Budweiser InBev}{Shanghai, China}{Trade Marketing Intern}{Jun.~2025 -- Present}
\begin{itemize}
  \resumeItem{Streamlined store compliance standards, improving summer campaign compliance by 10\% and cutting customer complaints by 93\%.}
  \resumeItem{Developed tiered incentives that drove sign-ups across 7M+ stores and lifted orders from 1.3M to 5.9M cases (\texttt{+78\%}).}
  \resumeItem{Led data collection and analysis to guide resource allocation and ROI tracking for regional activations.}
  \resumeItem{Built Power BI dashboards covering 70,000+ stores to enhance visibility for business units.}
\end{itemize}
\vspace{0.4em}
\resumeSubsection{L'Or\'eal China}{Shanghai, China}{Employer Branding Intern}{Aug.~2024 -- Jun.~2025}
\begin{itemize}
  \resumeItem{Recruited a 16-member Employer Branding student team to amplify campus presence.}
  \resumeItem{Organized four major events, secured three sponsorships, and delivered 30,000+ views via influencer collaborations, converting 18\% of attendees into follow-up events and adding 2,500+ potential applicants.}
  \resumeItem{Managed recruitment platform accounts that achieved 29\% higher engagement than the previous top-performing team and 67\% above the cohort average.}
\end{itemize}
\vspace{0.4em}
\resumeSubsection{DERMO IONIQ}{France}{Marketing Strategy Intern}{Dec.~2024 -- May~2025}
\begin{itemize}
  \resumeItem{Created customized product kits aligned to skin needs, raising website conversion by 20\%.}
  \resumeItem{Launched an eco-friendly packaging initiative that cut production costs by 10\% while ensuring regulatory compliance.}
  \resumeItem{Executed social media and live-stream campaigns reaching 20M+ consumers with 8\% engagement, boosting brand awareness.}
\end{itemize}

\resumeSection{Additional Leadership}
\resumeSubsection{The 11th Art Troupe, Renmin University of China}{Suzhou, China}{Deputy Head}{Sep.~2023 -- Aug.~2024}
\begin{itemize}
  \resumeItem{Exceeded annual event targets by two through data-informed program design, including a lawn music festival and drama productions that increased participation by 20\% year-on-year across 2,000+ surveyed students.}
  \resumeItem{Implemented standardized event SOPs and a cross-department resource pool, shortening preparation time by 30\%, reducing costs by 15\%, and generating 5,000+ engagements.}
\end{itemize}

\resumeSection{Skills \& Interests}
\begin{itemize}[leftmargin=1.2em]
  \resumeItem{\textbf{Languages:} Mandarin Chinese (Native), English (IELTS~6.5), French (B1).}
  \resumeItem{\textbf{Technical:} Microsoft Office, Adobe Premiere, Adobe Photoshop, Canva, SPSS, R, Stata, SQL, SAS, Tableau, Power BI.}
  \resumeItem{\textbf{Hobbies:} Piano, Table Tennis.}
\end{itemize}

\end{document}
